Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-07 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

\begin{abstract}
\textcolor{blue}{In the current scenario, energy demand rises by 1.3\% each year to 2040, and photovoltaic (PV) systems} have emerged as an alternative to the fossil or nuclear fuel energy generation. The use of formal methods for PV systems is a new subject with significant research spanning only five years. Here we develop and evaluate \textcolor{blue}{an} automated synthesis technique to obtain optimal sizing \textcolor{blue}{of PV systems based on Life Cycle Cost (LCC) analysis. The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement, operation, and maintenance costs over $20$ years. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the optimization}. We advocate that \textcolor{blue}{our technique} has various advantages if compared to off-the-shelf optimization tools available in the market \textcolor{blue}{for PV systems}. Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different software verifiers are evaluated to check performance and soundness. We also compare our approach with a commercial tool specialized in PV systems optimization. Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness. 
\keywords{Formal Synthesis \and Software Verification \and Solar Photovoltaic Systems \and Cyber-Physical Systems.}
\end{abstract}

@@

@@

\noindent where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current rates. \textcolor{blue}{In this study, we will use a $C_{installation}$ equivalent to 5\% of total equipment cost and a $C_{PWO\&M}$ equal to U\$ 289.64/year according to Amazon State literature data~\cite{Agrener2013}.}

@@

If our algorithm does not find a feasible solution among the item of equipment that was provided for our {\sc Synthesize} phase, then the result is unsatisfiable (\textit{UNSAT}). In particular, the program finishes without finding a solution, indicating that it was unable to combine the specific items of equipment to create a feasible solution. 
%
The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution for the constraints and user requirements. The problem for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase. 
%
Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
The verification engines transform the Algorithm~\ref{alg:opt-algorithm} into the Boolean expressions that are passed to the solver to verify ($C \wedge \neg P$), as described online.\footnote{\url{https://tinyurl.com/yajfmavl}}

@@

\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) are not the same \textcolor{red}{add citation}. Therefore, the comparison must take this issue into account.}

>>>>

\begin{abstract}
\textcolor{blue}{In the current scenario, energy demand rises by 1.3\% each year to 2040, and photovoltaic (PV) systems} have emerged as an alternative to the fossil or nuclear fuel energy generation. The use of formal methods for PV systems is a new subject with significant research spanning only five years. Here we develop and evaluate \textcolor{blue}{an} automated synthesis technique to obtain optimal sizing \textcolor{blue}{of PV systems based on Life Cycle Cost (LCC) analysis. The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement, operation, and maintenance costs over $20$ years. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the PV sizing optimization}. We advocate that \textcolor{blue}{our technique} has various advantages if compared to off-the-shelf optimization tools available in the market \textcolor{blue}{for PV systems}. Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different software verifiers are evaluated to check performance and soundness. We also compare our approach with a commercial tool specialized in PV systems optimization. Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness. 
\keywords{Formal Synthesis \and Software Verification \and Solar Photovoltaic Systems \and Cyber-Physical Systems.}
\end{abstract}

@@

\textcolor{blue}{Summarizing: Our proposal is a technique based on CEGIS and we aim to synthesize the optimal solution of a PV system. Therefore, our technique produces an optimization.}

@@

\noindent where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current rates. \textcolor{blue}{In this study, we will use a $C_{installation}$ equivalent to 5\% of total equipment cost and a $C_{PWO\&M}$ equal to U\$ 289.64/year according to Amazon State literature data~\cite{Agrener2013}; and a LCC lifetime analysis of 20 years.}

@@

If our algorithm does not find a feasible solution among the item of equipment that was provided for our {\sc Synthesize} phase, then the result is unsatisfiable (\textit{UNSAT}). In particular, the program finishes without finding a solution, indicating that it was unable to combine the specific items of equipment to create a feasible solution. 
%
The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution for the constraints and user requirements. The problem for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase.

\textcolor{blue}{Summarizing: We use four non-deterministic variables to index four matrices with complete datasheet information from an equipment item. We have four variables and four matrices: one to PV panels, one to batteries, one to the inverter, and one to the charge controller. Those non-deterministic variables are used during the search for the feasible solution and controlled by the statements \textbf{assume}. The candidate solution is proposed in the phase {\sc Synthesize} of the technique. For the {\sc Verify} phase, we performed a linear search for the lowest cost, and the result is based on FAIL or SUCCESS check from a cost that is linearly incremented in this model. The model checking is used during this {\sc Verify} phase. If the process produces FAIL, then an optimal solution is found. If SUCCESS is presented, i.e. the property holds, there is no feasible solution from the equipment list provided by the technique.}
%
Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
The verification engines transform the Algorithm~\ref{alg:opt-algorithm} into the Boolean expressions that are passed to the solver to verify ($C \wedge \neg P$), as described online.\footnote{\url{https://tinyurl.com/yajfmavl}}

@@

\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) are not the same \cite{Alsadi2018}. Therefore, the comparison must take this issue into account.}

### 2020-07-07 Tex/CAV2019/replyVSTTEJUNE2020.tex
VSTTE rebuttal

\begin{resposta} 
We thank the reviewer again for this insightful comment. We had to revise some specific parts of the paper, where the CEGIS technique, or optimization appeared (Abstract, Introduction, and Background sections). Our proposal is a technique based on CEGIS when considering the use of synthesis and automated verification. We aim to synthesize the optimal solution of a PV system (i.e., the technique produces an optimization). We expect that the revised sections can clarify the issue. \textcolor{red}{Which changes did you implement? please specify them here}.
\end{resposta}

@@

\begin{resposta} 
\textcolor{red}{where do we address this comment? Please indicate the section.}
We use four nondeterministic variables to hold four matrices with complete datasheet information from an equipment item. We have four variables and four matrices: one to PV panels, one to batteries, one to the inverter, and one to the charge controller. Those nondeterministic variables are used during the search for the feasible solution and controlled by the statements \textbf{assume}. The candidate solution is proposed in the phase {\sc Synthesize} of the technique. For the {\sc Verify} phase, we performed a linear search for the lowest cost, and the result is based on FAIL or SUCCESS check from a cost that is linearly incremented in this model. The model checking is used during this {\sc Verify} phase. If the process produces FAIL, then an optimal solution is found. If SUCCESS is provided, there is no feasible solution from the equipment list provided by the technique. We added a future work at the end of the CONCLUSIONS section, related to the possibility of speeding up the {\sc Verify} phase through binary search or even using specific optimization targeted solvers (as $\nu Z$).
\end{resposta}

>>>>

\begin{resposta} 
We thank the reviewer again for this insightful comment. We had to revise some specific parts of the paper, where the CEGIS technique, or optimization appeared (Abstract, and Background sections). Our proposal is a technique based on CEGIS when considering the use of synthesis and automated verification. We aim to synthesize the optimal solution of a PV system (i.e., the technique produces an optimization). We expect that the revised sections below can clarify the issue, besides the next answer related to Algorithm 1.

Into the Abstract section now we have: "Here we develop and evaluate an automated synthesis technique to obtain optimal sizing of PV systems based on Life Cycle Cost (LCC) analysis. The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement, operation, and maintenance costs over $20$ years. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the PV sizing optimization."

In the Background section now we have: "Summarizing: Our proposal is a technique based on CEGIS and we aim to synthesize the optimal solution of a PV system. Therefore, our technique produces an optimization."

\textcolor{red}{The two above sentences are new}.

\end{resposta}

@@

\begin{resposta} 
We use four non-deterministic variables to index four matrices with complete datasheet information from an equipment item. We have four variables and four matrices: one to PV panels, one to batteries, one to the inverter, and one to the charge controller. Those non-deterministic variables are used during the search for the feasible solution and controlled by the statements \textbf{assume}. The candidate solution is proposed in the phase {\sc Synthesize} of the technique. For the {\sc Verify} phase, we performed a linear search for the lowest cost, and the result is based on FAIL or SUCCESS check from a cost that is linearly incremented in this model. The model checking is used during this {\sc Verify} phase. If the process produces FAIL, then an optimal solution is found. If SUCCESS is presented, i.e. the property holds, there is no feasible solution from the equipment list provided by the technique. \textcolor{red}{This explanation was included at page 9, in the end of section "Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems".}
We added a future work at the end of the CONCLUSIONS section as well, related to the possibility of speeding up the {\sc Verify} phase through binary search or even using specific optimization targeted solvers (as $\nu Z$).
\end{resposta}
